Bumble bees and wildflowers along an elevational climate gradient exhibit niche

### 2020-07-08 analyses/FL_abund_GAM.Rmd
update

### Call models
weighted_fl_abundance.2010.qp <- bam(fl.abund.wt ~ bb.sp + te(yday, elev.mean, 
                                                            by = bb.sp,
                                                            bs= c("tp", "tp"), 
                                                            k=c(10, 10), m=1),
                        data = filter(fl_abund_wt, year == 2010),
                        discrete = TRUE,
                        family = "quasipoisson",
                        method = "fREML") %>% getViz()

@@

weighted_fl_abundance.2010.qp2 <- bam(sqrt(fl.abund.wt) ~ bb.sp + te(yday, elev.mean, 
                                                            by = bb.sp,
                                                            bs= c("tp", "tp"), 
                                                            k=c(10, 10), m=1),
                        data = filter(fl_abund_wt, year == 2010),
                        discrete = TRUE,
                        family = "quasipoisson",
                        method = "fREML") %>% getViz()

@@

weighted_fl_abundance.2011.qp <- bam(fl.abund.wt ~ bb.sp + te(yday, elev.mean, 
                                                            by = bb.sp,
                                                            bs= c("tp", "tp"), 
                                                            k=c(10, 10), m=1),
                        data = filter(fl_abund_wt, year == 2011),
                        discrete = TRUE,
                        family = "quasipoisson",
                        method = "fREML") %>% getViz()

@@

weighted_fl_abundance.2011.qp2 <- bam(sqrt(fl.abund.wt) ~ bb.sp + te(yday, elev.mean, 
                                                            by = bb.sp,
                                                            bs= c("tp", "tp"), 
                                                            k=c(10, 10), m=1),
                        data = filter(fl_abund_wt, year == 2011),
                        discrete = TRUE,
                        family = "quasipoisson",
                        method = "fREML") %>% getViz()

@@

weighted_fl_abundance.2012.qp <- bam(fl.abund.wt ~ bb.sp + te(yday, elev.mean, 
                                                            by = bb.sp,
                                                            bs= c("tp", "tp"), 
                                                            k=c(10, 10), m=1),
                        data = filter(fl_abund_wt, year == 2012),
                        discrete = TRUE,
                        family = "quasipoisson",
                        method = "fREML") %>% getViz()

@@

weighted_fl_abundance.2012.qp2_re <- bam(sqrt(fl.abund.wt) ~ s(bb.sp, bs = "re") + 
                                        management + 
                                        te(yday, elev.mean, 
                                           by = bb.sp,
                                           bs= c("tp", "tp"), 
                                           k=c(10, 10), m=1),
                        data = filter(fl_abund_wt, year == 2012),
                        discrete = TRUE,
                        select = TRUE,
                        family = "quasipoisson",
                        method = "fREML") %>% getViz()

check.gamViz(weighted_fl_abundance.2012.qp2_re)
summary(weighted_fl_abundance.2012.qp2_re)
print(plot(weighted_fl_abundance.2012.qp2_re, allTerms = TRUE), pages = 4)

weighted_fl_abundance.2012.qp2_p <- bam(sqrt(fl.abund.wt) ~ bb.sp + management + 
                                        te(yday, elev.mean, 
                                           by = bb.sp,
                                           bs= c("tp", "tp"), 
                                           k=c(10, 10), m=1),
                        data = filter(fl_abund_wt, year == 2012),
                        discrete = TRUE,
                        family = "quasipoisson",
                        method = "fREML") %>% getViz()

check.gamViz(weighted_fl_abundance.2012.qp2_p)
summary(weighted_fl_abundance.2012.qp2_p)
print(plot(weighted_fl_abundance.2012.qp2_p, allTerms = TRUE), pages = 4)

weighted_fl_abundance.qp2 <- bam(sqrt(fl.abund.wt) ~ bb.sp + year + te(yday, elev.mean, 
                                                            by = bb.sp,
                                                            bs= c("tp", "tp"), 
                                                            k=c(10, 10), m=1),
                        data = fl_abund_wt,
                        discrete = TRUE,
                        family = "quasipoisson",
                        method = "fREML") %>% getViz()

check.gamViz(weighted_fl_abundance.qp2)
summary(weighted_fl_abundance.qp2)
print(plot(weighted_fl_abundance.qp2 , allTerms = TRUE), pages = 4)

@@

v <- c(10,9, 5, 8,7)
v.rank = rank(v)

ggplot(mismatch, aes(fl.abund.wt.rank, bb.abund.rank)) +
  geom_point() +
  facet_wrap(~bb.sp)

>>>>

### Call models
weighted_fl_abundance.2010.qp <- bam(fl.abund.wt ~ s(bb.sp, bs = "re") + management + slope.est + te(yday, elev.mean, 
                                                            by = bb.sp,
                                                            bs= c("tp", "tp"), 
                                                            k=c(10, 10), m=1),
                        data = filter(fl_abund_wt, year == 2010),
                        discrete = TRUE,
                        family = "quasipoisson",
                        select = TRUE,
                        method = "fREML") %>% getViz()

@@

weighted_fl_abundance.2010.qp2 <- bam(sqrt(fl.abund.wt) ~ s(bb.sp, bs = "re") + management + slope.est + te(yday, elev.mean, 
                                                            by = bb.sp,
                                                            bs= c("tp", "tp"), 
                                                            k=c(10, 10), m=1),
                        data = filter(fl_abund_wt, year == 2010),
                        discrete = TRUE,
                        family = "quasipoisson",
                        select = TRUE,
                        method = "fREML") %>% getViz()

@@

weighted_fl_abundance.2011.qp <- bam(fl.abund.wt ~ s(bb.sp, bs = "re") + management + slope.est + te(yday, elev.mean, 
                                                            by = bb.sp,
                                                            bs= c("tp", "tp"), 
                                                            k=c(10, 10), m=1),
                        data = filter(fl_abund_wt, year == 2011),
                        discrete = TRUE,
                        family = "quasipoisson",
                        select = TRUE,
                        method = "fREML") %>% getViz()

@@

weighted_fl_abundance.2011.qp2 <- bam(sqrt(fl.abund.wt) ~ s(bb.sp, bs = "re") + management + slope.est + te(yday, elev.mean, 
                                                            by = bb.sp,
                                                            bs= c("tp", "tp"), 
                                                            k=c(10, 10), m=1),
                        data = filter(fl_abund_wt, year == 2011),
                        discrete = TRUE,
                        family = "quasipoisson",
                        select = TRUE,
                        method = "fREML") %>% getViz()

@@

weighted_fl_abundance.2012.qp <- bam(fl.abund.wt ~ s(bb.sp, bs = "re") + management + slope.est + te(yday, elev.mean, 
                                                            by = bb.sp,
                                                            bs= c("tp", "tp"), 
                                                            k=c(10, 10), m=1),
                        data = filter(fl_abund_wt, year == 2012),
                        discrete = TRUE,
                        family = "quasipoisson",
                        select = TRUE,
                        method = "fREML") %>% getViz()

@@

@@

ggplot(mismatch, aes(fl.abund.wt, bb.abund)) +
  geom_point() +
  facet_wrap(~bb.sp)

### 2020-07-08 analyses/beta_diversity.Rmd
update

### Load site data
```{r, include=FALSE, echo=FALSE}
site_data <- read_csv("../processed_data/site_data.csv") %>%
  dplyr::select(-c(slope.calc, slope.est, elev.min, elev.max, temp.mean)) %>% # drop these variables
  mutate(elev.class = factor(elev.class, levels = c("oben", "mitte", "unten")),
         elev.class2 = factor(elev.class2, levels = c("high", "mid", "low"))) %>% # turn elav.class into an ordered factor %>%
  semi_join(read_csv("../processed_data/network.csv"), by = "site")  %>%
  left_join(gdd_total, by = "site")

### A quick little analysis
ggplot(site_data, aes(elev.mean, gdd.total, color = year)) +
  geom_point() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 5)) +
  ylab("Total GDD")

# intercept only model
gdd_year.gam1 <- gam(gdd.total ~ s(elev.mean) + year,
                    data = site_data) %>% getViz()
summary(gdd_year.gam1)
check.gamViz(gdd_year.gam1)
plot(gdd_year.gam1)

# factor smooth model
gdd_year.gam2 <- gam(gdd.total ~ s(elev.mean, year, bs = "fs", k = 5),
                    data = site_data) %>% getViz()
summary(gdd_year.gam2)
check.gamViz(gdd_year.gam2)
plot(gdd_year.gam2)

# AIC
AIC(gdd_year.gam1, gdd_year.gam2)

site_pairwise_distance_t <- site_data %>%
  ungroup() %>%
  dplyr::select(site, lat, lon) %>%
  unique() %>%
  st_as_sf(coords = c("lon", "lat")) %>%
  st_set_crs(4326) %>%
  st_distance() %>%
  data.frame()

colnames(site_pairwise_distance_t) <- unique(site_data$site)
rownames(site_pairwise_distance_t) <- unique(site_data$site)

site_pairwise_distance <- site_pairwise_distance_t %>%
  rownames_to_column("site1") %>%
  pivot_longer(names_to = "site2", values_to = "distance", -site1)
```

### Load network and survey data and generate site.year and site.month.year webs
```{r}
bb_traits <- read_csv("../processed_data/bb_traits.csv") %>%
  dplyr::select(subgenus, bb.sp, pbl.w, pbl.w.class)

fl_traits <- read.csv("../processed_data/floral_k_type_nom_fix.csv") %>%
  dplyr::select(plant.sp, k.type) %>%
  mutate(k.type.s = str_extract(k.type, "[-+]?[0-9]*\\.?[0-9]+"),
         k.type.ss = str_extract(k.type, "[-+]?[0-9]*"))

fl_tax <- read_csv("../processed_data/floral_tax.csv")

breaks <- read_csv("./output/breaks.csv") %>%
  mutate(year = factor(year))

net <- read_csv("../processed_data/network.csv") %>%
  unite(site.year, site, year, sep = "_", remove = FALSE) %>% # create site.year field that can later be split back up
  unite(site.date, site, date, sep = "_", remove = FALSE) %>%
  mutate(year = factor(year)) %>% # convert year to factor
  full_join(bb_traits, by = c("bb.sp" = "bb.sp")) %>%
  left_join(site_data, by = "site") %>%
  left_join(gdd, by = c("site", "date")) %>%
  left_join(breaks, by = c("site", "year")) %>%
  left_join(fl_traits) %>%
  left_join(fl_tax, by = "plant.genus") %>%
  ungroup() %>%
  mutate(phase = case_when(
    gdd.cum < break1.gdd ~ "founding",
    gdd.cum >= break1.gdd & gdd.cum < break2.gdd ~ "buildup",
    gdd.cum > break2.gdd ~ "reproductive"
  )) %>%
  mutate(phase = factor(phase, levels = c("founding", "buildup", "reproductive"))) %>%
  arrange(site, date)

@@

web_site <- net %>%
  group_by(site, bb.sp, plant.sp) %>%
  summarize(freq = n()) %>% 
  dplyr::select(higher = bb.sp, lower = plant.sp, webID = site, freq) %>% # rename columns to match bipartite's expectations
  data.frame() %>% # convert to data frame
  frame2webs() # convert to to bipartite web

survey <- read_csv("../processed_data/floral_survey.csv") %>%
  mutate(year = factor(year)) %>% # convert year to factor
  semi_join(net, by = "plant.sp") %>% # Consider only plants visited at a given site-date
  left_join(gdd, by = c("site", "date", "year")) %>%
  left_join(breaks, by = c("site", "year")) %>%
  left_join(site_data, by = "site") %>%
  left_join(fl_traits) %>%
  left_join(fl_tax) %>%
  ungroup() %>%
  mutate(phase = case_when(
    gdd.cum < break1.gdd ~ "founding",
    gdd.cum >= break1.gdd & gdd.cum < break2.gdd ~ "buildup",
    gdd.cum > break2.gdd ~ "reproductive"
  )) %>%
  mutate(phase = factor(phase, levels = c("founding", "buildup", "reproductive"))) %>%
  arrange(site, date)
```

@@

beta_site <- betalinkr_multi(array_site, partition.st = TRUE, partition.rr = TRUE) %>%
  as_tibble() %>%
  rename(site1 = i) %>%
  rename(site2 = j) %>%
  left_join(site_data, by = c("site1" = "site")) %>%
  dplyr::select(site1, site2, S, OS, WN, ST, 
         ST.l, ST.h, ST.lh, WN.repl, OS.repl, WN.rich, OS.rich, 
         elev1 = elev.mean, man1 = management, lon1 = lon, lat1 = lat) %>%
  left_join(site_data, by = c("site2" = "site")) %>%
  dplyr::select(site1, site2, S, OS, WN, ST, 
         ST.l, ST.h, ST.lh, WN.repl, OS.repl, WN.rich, OS.rich, 
         elev1, elev2 = elev.mean, man1, man2 = management, lon1, lat1, lon2 = lon, lat2 = lat) %>%
  mutate(elev.diff = abs(elev1 - elev2),
         mean.elev = (elev1 + elev2)/2,
         man.diff = case_when(
           man1 == man2 ~ FALSE,
           man1 != man2 ~ TRUE
         )) %>%
  gather(metric, value, -c(site1, site2, elev1, elev2, elev.diff, 
                           man1, man2, man.diff, mean.elev, lon1, lat1, lon2, lat2)) %>%
  left_join(site_pairwise_distance) %>%
  mutate(metric.class = case_when(
    metric %in% c("WN", "ST", "OS", "S") ~ "aggregate",
    metric %in% c("WN.repl", "WN.rich") ~ "WN.partition",
    metric %in% c("ST.h", "ST.l", "ST.lh") ~ "ST.partition",
    metric %in% c("OS.repl", "OS.rich") ~ "OS.partition"
  ))

@@

# And not much of a pattern in response to geographical distance
ggplot(beta_site, 
       aes(as.numeric(distance), value, color = metric)) +
  geom_smooth()

@@

### Let's look at floral survey diversity patterns
```{r}
survey_bioData <- survey %>%
  filter(flower.cover > 0) %>%
  mutate(plant.sp = str_replace_all(plant.sp, " ", "_")) %>%
  group_by(site, plant.sp) %>%
  summarize(cover = mean(flower.cover)) %>%
  spread(plant.sp, cover) %>%
  replace(is.na(.), 0)

@@

### And now Bombus diversity patterns
```{r}
BB_bioData <- net %>%
  group_by(site, date, bb.sp) %>%
  summarize(count = n()) %>%
  group_by(site, date) %>%
  mutate(prop = count/sum(count)) %>%
  group_by(site, bb.sp) %>%
  summarize(abund = mean(prop)) %>%
  spread(bb.sp, abund) %>%
  replace(is.na(.), 0)

>>>>

### Load site data
```{r, include=FALSE, echo=FALSE}
site_data <- read_csv("../processed_data/site_data.csv") %>%
  dplyr::select(-c(slope.calc, slope.est, elev.min, elev.max, temp.mean)) %>% # drop these variables
  mutate(elev.class = factor(elev.class, levels = c("oben", "mitte", "unten")),
         elev.class2 = factor(elev.class2, levels = c("high", "mid", "low"))) %>% # turn elav.class into an ordered factor
  semi_join(read_csv("../processed_data/network.csv"), by = "site")

# %>%
#   left_join(gdd_total, by = "site")

### Plot total GDD
ggplot(site_data, aes(elev.mean, gdd.total, color = year)) +
  geom_point() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 5)) +
  ylab("Total GDD")
```

### Load network and survey data and generate site.year and site.month.year webs
```{r}
# bb_traits <- read_csv("../processed_data/bb_traits.csv") %>%
#   dplyr::select(subgenus, bb.sp, pbl.w, pbl.w.class)
# 
# fl_traits <- read.csv("../processed_data/floral_k_type_nom_fix.csv") %>%
#   dplyr::select(plant.sp, k.type) %>%
#   mutate(k.type.s = str_extract(k.type, "[-+]?[0-9]*\\.?[0-9]+"),
#          k.type.ss = str_extract(k.type, "[-+]?[0-9]*"))

# fl_tax <- read_csv("../processed_data/floral_tax.csv") 
# 
# breaks <- read_csv("./output/breaks.csv") %>%
#   mutate(year = factor(year))

net <- read_csv("../processed_data/network.csv") %>%
  unite(site.year, site, year, sep = "_", remove = FALSE) %>% # create site.year field that can later be split back up
  unite(site.date, site, date, sep = "_", remove = FALSE) %>%
  mutate(year = factor(year)) %>% # convert year to factor
  #full_join(bb_traits, by = c("bb.sp" = "bb.sp")) %>%
  left_join(site_data, by = "site") %>%
  #left_join(gdd, by = c("site", "date")) %>%
  #left_join(breaks, by = c("site", "year")) %>%
  #left_join(fl_traits) %>%
  #left_join(fl_tax, by = "plant.genus") %>%
  ungroup() %>%
  #mutate(phase = case_when(
    # gdd.cum < break1.gdd ~ "founding",
    # gdd.cum >= break1.gdd & gdd.cum < break2.gdd ~ "buildup",
    # gdd.cum > break2.gdd ~ "reproductive"
  #)) %>%
  #mutate(phase = factor(phase, levels = c("founding", "buildup", "reproductive"))) %>%
  arrange(site, date)

survey <- read_csv("../processed_data/floral_survey.csv") %>%
  semi_join(net, by = "plant.sp") %>% # Consider only plants visited (anytime anywhere, not specifically for a given site*date)
  dplyr::select(site, date, plant.sp, flower.cover)

@@

web_site <- net %>%
  group_by(site, bb.sp, plant.sp) %>%
  summarize(freq = n()) %>% 
  dplyr::select(higher = bb.sp, lower = plant.sp, webID = site, freq) %>% # rename columns to match bipartite's expectations
  data.frame() %>% # convert to data frame
  frame2webs() # convert to to bipartite web
```

@@

beta_site <- betalinkr_multi(array_site, partition.st = TRUE, partition.rr = TRUE) %>%
  as_tibble() %>%
  rename(site1 = i) %>%
  rename(site2 = j) %>%
  left_join(site_data, by = c("site1" = "site")) %>%
  dplyr::select(site1, site2, S, OS, WN, ST, 
         ST.l, ST.h, ST.lh, WN.repl, OS.repl, WN.rich, OS.rich, 
         elev1 = elev.mean, man1 = management, lon1 = lon, lat1 = lat) %>%
  left_join(site_data, by = c("site2" = "site")) %>%
  dplyr::select(site1, site2, S, OS, WN, ST, 
         ST.l, ST.h, ST.lh, WN.repl, OS.repl, WN.rich, OS.rich, 
         elev1, elev2 = elev.mean, man1, man2 = management, lon1, lat1, lon2 = lon, lat2 = lat) %>%
  mutate(elev.diff = abs(elev1 - elev2),
         mean.elev = (elev1 + elev2)/2,
         man.diff = case_when(
           man1 == man2 ~ FALSE,
           man1 != man2 ~ TRUE
         )) %>%
  gather(metric, value, -c(site1, site2, elev1, elev2, elev.diff, 
                           man1, man2, man.diff, mean.elev, lon1, lat1, lon2, lat2)) %>%
  #left_join(site_pairwise_distance) %>%
  mutate(metric.class = case_when(
    metric %in% c("WN", "ST", "OS", "S") ~ "aggregate",
    metric %in% c("WN.repl", "WN.rich") ~ "WN.partition",
    metric %in% c("ST.h", "ST.l", "ST.lh") ~ "ST.partition",
    metric %in% c("OS.repl", "OS.rich") ~ "OS.partition"
  ))

write_csv(beta_site, "../analyses/output/beta_site.csv")

@@

# # And not much of a pattern in response to geographical distance
# ggplot(beta_site, 
#        aes(as.numeric(distance), value, color = metric)) +
#   geom_smooth()

@@

### Let's look at floral survey diversity patterns
```{r}
survey_bioData <- survey %>%
  filter(flower.cover > 0) %>%
  mutate(plant.sp = str_replace_all(plant.sp, " ", "_")) %>%
  group_by(site, plant.sp) %>%
  summarize(cover = sum(flower.cover)) %>%
  spread(plant.sp, cover) %>%
  replace(is.na(.), 0)

@@

### And now Bombus diversity patterns
```{r}
BB_bioData <- net %>%
  group_by(site, date, bb.sp) %>%
  summarize(count = n()) %>%
  group_by(site, date) %>%
  mutate(prop = count/sum(count)) %>%
  group_by(site, bb.sp) %>%
  summarize(abund = sum(prop)) %>%
  spread(bb.sp, abund) %>%
  replace(is.na(.), 0)

### 2020-07-08 writing/manuscript_v3.Rmd
update

*[paragraph about Bombus being cold-adapted and generally distributed in high latitude or high elevation habitats]*
Bumble bees (Hymenoptera: *Bombus* spp.) are cold-adapted species that likely originated in cooling climate of the Eocene-Oligocene boundary (34 mya) and now distributed mainly at higher latitudes and elevations [@Hines2008-er].

@@

**Methods**
*Study sites*
*Sampling*
Because the frequency, duration, and seasonal interval of sampling varied across years, we model each year separately in all analyses.

*Growing degree day analysis*
*Diversity modeling*
- GDM
*Abundance modeling*
To represent floral abundance from the perspective of foraging bumble bees, we multiplied raw floral abundance by species-specific "preference" coefficients. The latter were calculated by regressing log-transformed mean proportional visitation against log-transformed mean proportional flower cover for all possible pairs of plant and bumble bee species, then extracting and exponentiating the residuals for each bee-plant pair (Supplemental Material). Using the R package mgcv, preference-weighted floral abundance was modeled using hierarchical generalized additive models consisting of a 2D tensor-product smooth of elevation and time (day-of-year), with bumble bee species as both a "by" smoothing factor and a random intercept term (Supplemental Material).

*Network analysis*
- Bootstrapping
- Network metrics

**Results**
*Diversity: Turnover asymmetry between bumble bees and floral hosts*
Beta diversity analysis

*Abundance: Heterogeneous distribution of bumble bees and floral hosts over elevation x time surface*
- Contrast the broadly heterogeneous distribution of habitat generalist BBs to the restricted distribution of high-elevation specialists
- Heterogeneous distribution of generalists indicates either or both movement along the elevation gradient or heterogeneous colonization along the elevation gradient.
- Concentration of preferred resources near the tree line
- Habitat specialists are often separated from their preferred host plants, probably due to thermal constraints, possibly due to competition, maybe both
- Habitat generalists vary in the degree to which their distribution matches that of their preferred hosts, suggesting that they are constrained by colonization, competition, or both.

@@

At around 1600 m, just below the tree line where the forest starts to thin, there seems to be a uniquely important elevation band. For many bumble bee species in our system, this is where preference-weighted floral resource abundance is highest. For a few species, it is the only peak in preference-weighted floral abundance.

There also seems to be a consistent peak in preference-weighted floral abundance around 1000 m.

>>>>

In mountain habitats, bumble bees (Hymenoptera: *Bombus* spp.) and their floral hosts provide an ideal study system in which to explore the effects of climate at both the basic level of species' distribution and abundance and the higher level of interaction network structure and dynamics.

*[paragraph about Bombus being cold-adapted and generally distributed in high latitude or high elevation habitats]*
Bumble bees (Hymenoptera: *Bombus* spp.) are cold-adapted species that likely originated in cooling climate of the Eocene-Oligocene boundary (34 mya) and are  now distributed mainly at higher latitudes and elevations [@Hines2008-er].

@@

**Methods**
*Study sites and sampling protocol*

*Diversity and abundance modeling*
To represent floral abundance from the perspective of foraging bumble bees, we multiplied raw floral abundance by species-specific "preference" coefficients. The latter were calculated by regressing log-transformed mean proportional visitation against log-transformed mean proportional flower cover for all possible pairs of plant and bumble bee species, then extracting and exponentiating the residuals for each bee-plant pair (Supplemental Material). Using the R package mgcv, preference-weighted floral abundance was modeled using hierarchical generalized additive models consisting of a 2D tensor-product smooth of elevation and time (day-of-year), with bumble bee species as both a "by" smoothing factor and a random intercept term (Supplemental Material).

*Network analysis*
- Interaction beta-diversity
- Network metrics (with bootstrapping)

**Results**
*Diversity: Turnover asymmetry between bumble bees and floral hosts*
Interaction beta diversity between pairs of sites was generally high, and

```{r}
beta_site <- read_csv("../analyses/output/beta_site.csv") %>%
  mutate(metric.class = factor(metric.class))

ggplot(beta_site, 
       aes(elev.diff, value, color = metric)) +
  geom_point(alpha = 0.05) +
  geom_smooth() +
  facet_wrap(~metric.class)

ggplot(filter(beta_site, metric.class == "aggregate" & metric != "S"), 
       aes(elev.diff, value, color = metric)) +
  geom_point(alpha = 0.05) +
  geom_smooth(method = "lm")

ggplot(filter(beta_site, metric.class == "ST.partition" & metric != "S"), 
       aes(elev.diff, value, color = metric)) +
  geom_point(alpha = 0.05) +
  geom_smooth(method = "lm", formula = y ~ poly(x, 2))
```

*Abundance and diversity: Heterogeneous distribution of bumble bees and floral hosts over elevation x time surface*
- Contrast the broadly heterogeneous distribution of habitat generalist BBs to the restricted distribution of high-elevation specialists
- Heterogeneous distribution of generalists indicates either or both movement along the elevation gradient or heterogeneous colonization along the elevation gradient.
- Concentration of preferred resources near the tree line
- Habitat specialists are often separated from their preferred host plants, probably due to thermal constraints, possibly due to competition, maybe both
- Habitat generalists vary in the degree to which their distribution matches that of their preferred hosts, suggesting that they are constrained by colonization, competition, or both.

@@

At around 1600 m, just below the tree line where the forest starts to thin, there seems to be a uniquely important elevation band. For many bumble bee species in our system, this is where preference-weighted floral resource abundance is highest. For a few species, it is the only peak in preference-weighted floral abundance. "This 'range over-lap effect' is particularly pronounced in the zone of gradual or patch-wise transition from montane forests to alpine vegetation." [@Becker2007-cg]

There also seems to be a consistent peak in preference-weighted floral abundance around 1000 m. The slope breaks from the valley floor around 800-900 m, so 1000 m is low-mid slope.
